---
title: "ptools vignette"
author: "Camille Bonamy"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


This packages provides basis R and Hadoop wrapper function to handle file movement in pipelines.

This vignette will provide one example of specific implementation. You can modify the number of steps and organisation of physic files / tabulated data to fit your expectation.

### Organisation

The flat files (e.g csv) is processed from landing -> data/raw -> data/intermediate -> data/final. Those folder will be used here :

* landing : to store and archive incoming data
* data/raw : to perform file type conversion if needed
* data/intermediate : to clean the data
* data/final : to clean even more ?

Let data_0.json be an incoming file to your hdfs. Then using


you convert them to csv file and move to data/raw.

Then you can do some cleaning / type conversion and store thme to intermediate :

Before performing maybe some pivot table :

Then you create (or recreate here) tables :

And you can perform joins.

Do you analysis

Clean even more, ML :

Markdown results

Shiny eventually.







Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
